### 2019-02-20 Chapters/Chapter2.tex
app d

As we discuss earlier, even tough the tight binding model is successful in describing the band structure of most solids, it fails in some cases. In strongly correlated electron systems, the effect of electron-electron Coulomb interactions is important, and this effect is neglected in \ref{TBModel}. The simplest way to take this effect into account is to consider the interaction of electrons in the same site only, that is, adding a term of the form $\text{U}\sum_i \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$:
\begin{equation}
\label{HH}
\hat{H} = -t\sum_{\langle i,j \rangle \sigma} \hat{c}^{\dagger}_{i\sigma}\hat{c}_{j\sigma} + \text{U}\sum_i \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
\end{equation}
This new term will add an energy $+\text{U}$ when a site is double occupied ($\hat{n}_{i\uparrow} = \hat{n}_{i\downarrow} = 1$) and will not contribute in the more normal case, that $\hat{n}_{i\uparrow} + \hat{n}_{i\downarrow} = 1$. The half-filled case is most commonly studied, this is the situation where the system has one electron per site (or it has half the maximum allowed number). This situation is simpler in many ways and it exhibits a lot of interesting phenomena (Mott insulating behavior, antiferromagnetic order, etc.). However, other cases have also been widely studied.

>>>>

As we discuss earlier, even tough the tight binding model is successful in describing the band structure of most solids, it fails in some cases. In strongly correlated electron systems, the effect of electron-electron Coulomb interactions is important, and this effect is neglected in \ref{TBModel}. The simplest way to take this effect into account is to consider the interaction of electrons in the same site only, that is, adding a term of the form $\text{U}\sum_i \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$:
\begin{equation}
\label{HH}
\hat{H} = -t\sum_{\langle i,j \rangle \sigma} \hat{c}^{\dagger}_{i\sigma}\hat{c}_{j\sigma} + \text{U}\sum_i \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
\end{equation}
Figure \ref{fig:Hubbard} shows a graphical representation of these parameters. This new term will add an energy $+\text{U}$ when a site is double occupied ($\hat{n}_{i\uparrow} = \hat{n}_{i\downarrow} = 1$) and will not contribute in the more normal case, that $\hat{n}_{i\uparrow} + \hat{n}_{i\downarrow} = 1$. The half-filled case is most commonly studied, this is the situation where the system has one electron per site (or it has half the maximum allowed number). This situation is simpler in many ways and it exhibits a lot of interesting phenomena (Mott insulating behavior, antiferromagnetic order, etc.). However, other cases have also been widely studied.

\begin{figure}
\centering
  \includegraphics[width=\linewidth]{../Figures/hubbard.png}
  \caption{Image from Scalettar's notes representing the kinetic term $t$ and the on-site interaction $\text{U}$ in the Hubbard model.} 
\label{fig:Hubbard}
\end{figure}
